Stat 400 Project

### 2021-11-30 Stat 400 proj.Rmd
commit bug

@@

``` {r}
simulator = function(start,b){
  current_infected = infected_idx(start)

>>>>

update_infected = function(indx,state){
  starting_values[,4] = state
}

counts = function(day,count){
  vals = c(day,count)
  return(vals)
}

@@

``` {r}
simulator = function(start,b,days){
  infected_df = cbind(c(1:days),c(rep(NA,days)))

  for(i in 1:days){
    current_infected = infected_idx(start)
    #list of neighbors close to infected with id, and distance from infected.

    #calculate
